Software Ticket Quality

### 2017-11-27 proposal/mprop.tex
Finish issue quality section of the lit review

@@

Even though we have discussed about quality in bug reports and how it can be
identified, we must also investigate if the platform where these bug reports 
reside (i.e. bug trackers) are properly fitting the software environment. 
The work of \citet{just2008towards} tries to find the answer to this question.
The authors launched a survey to developers from Eclipse, Mozilla and Apache
open source projects from which they received 175 comments back. Then, they
applied a card sort in order to organize the comments into hierarchies to 
deduce a higher level of abstraction and identify common patterns. In the end,
they ranked the top suggestions as follows:
  \begin{itemize}
    \item provide tool support for users to collect and prepare information that 
      developers need;
    \item find volunteers to translate bug reports filed in foreign languages;
    \item provide different user interfaces for each user level and give cues to 
      inexperienced reporters on what to report and best practices;
    \item reward reporters when they do a good job;
    \item integrate reputation into user profiles to mark experienced reporters;
    \item provide powerful and easy to use tools to search bug reports;
    \item encourage users to submit additional details (provide tools for merging 
      bugs).
  \end{itemize}

@@

\textbf{Analyzing and Relating Bug Report Data for Feature Tracking}\cite{fischer2003analyzing}:
\begin{itemize}
  \item \textbf{What were the goals?}
  The main goal of the paper was to analyze the proximity of software features based on modification and problem report data.
  \item \textbf{What was the method?}
  They employed a method to track features by analyzing and relating bug report data filtered from a release history database. Features are instrumented and tracked, relationships of modification and problem reports to these features are established, and tracked features are visualized to illustrate their otherwise hidden dependencies. 
  \item \textbf{What did they learn?}
  The authors’ approach suggest first to instrument and track features, then establish the relationships of modification and problem reports to these features and lastly visualize the tracked features for illustrating their non apparent dependencies. 
  \item \textbf{Relevance to our work}:
  This paper can give us insight into how bug reports can influence feature implementation throughout the lifetime of the ticket. 
\end{itemize}

\textbf{Duplicate Bug Reports Considered Harmful... 
Really}\cite{bettenburg2008duplicate}:
\begin{itemize}
  \item \textbf{What were the goals?}
  The authors wanted to test two main hypotheses, and these were: duplicate bug reports provide developers with information that was not present in the original report and the information in bug duplicates can improve automated triaging techniques. 
  \item \textbf{What was the method?}
  They collected big amounts of data from the Eclipse open source project in XML form. Then, they ran different kinds of textual and statistical analysis on the data to find answers to their research questions. 
  \item \textbf{What did they learn?}
  They reached the conclusion that bug duplicates contain information that is not present in the master reports. This additional data can be helpful for developers and it can also aid automated triaging techniques (e.g. decide who to assign a bug to). 
  \item \textbf{Relevance to our work}:
  The findings presented in this paper could potentially make us consider duplicate tickets in a different way (i.e. do not treat it as disposable but analyze it and see if it maybe adds more information to the original/master report). 
\end{itemize}

>>>>

Other interesting findings regarding the quality of a software project's tickets
are the ones elicited in \citet{bettenburg2008duplicate}. The authors examined
whether duplicate bug reports are actually harmful to a project or they add 
quality. They collected big amount of data from the Eclipse project and ran
various kind of textual and statistical analysis on the data to find answers.
They reached the conclusion that bug duplicates contain information that is not
present in the master reports. This additional data can be helpful for developers
and it can also aid automated triaging techniques.

@@

Having discussed automated linkage between source code files and bug reports, 
\citet{fischer2003analyzing} presents a way to track certain features from the
data residing in tickets. The authors employed a method to track features by 
analyzing and relating bug report data filtered from a release history database.
Features are then instrumented and tracked, relationships of modification and 
problem reports to these features are established, and tracked features are
visualized to illustrate their otherwise hidden dependencies. They managed to 
successfully visualize the tracked features and illustrate their non apparent
dependencies which can prove very useful in projects with a large number of
components.

Even though we have discussed about quality in bug reports, how it can be 
identified and what state-of-the-art techniques can be used to extract and 
link various components from tickets, we must also investigate if the platform 
where these bug reports 
reside (i.e. bug trackers) are properly fitting the software environment. 
The work of \citet{just2008towards} tries to find the answer to this question.
The authors launched a survey to developers from Eclipse, Mozilla and Apache
open source projects from which they received 175 comments back. Then, they
applied a card sort in order to organize the comments into hierarchies to 
deduce a higher level of abstraction and identify common patterns. In the end,
they ranked the top suggestions as follows:
  \begin{itemize}
    \item provide tool support for users to collect and prepare information that 
      developers need;
    \item find volunteers to translate bug reports filed in foreign languages;
    \item provide different user interfaces for each user level and give cues to 
      inexperienced reporters on what to report and best practices;
    \item reward reporters when they do a good job;
    \item integrate reputation into user profiles to mark experienced reporters;
    \item provide powerful and easy to use tools to search bug reports;
    \item encourage users to submit additional details (provide tools for merging 
      bugs).
  \end{itemize}

@@
